Performance Models for Data Transfers: A Case Study with Molecular Chemistry Kernels

### 2019-03-22 Article/article.tex
different heuristics and their favorable situation

   	\begin{figure}[htb]
   		\centering
   		\includegraphics[scale=0.07]{3PARToSched.jpg}
   		\caption{ \label{fig:firstSegment} First segment of Schedule $S$}
   	\end{figure}

@@

	\todo[inline]{SKumar: Evaluate different metrics for HF, Cholesky and CCSD applications}
	\todo[inline]{SKumar: decide metrics: ratio to optimal, percentage overlap, 100 - percentage non overlap}
		\item Machine description
		\item temporary data requirement
		\item Description of all kernels (Molecular Chemistry Kernels)
		\item Think about results and graphs (Most probably results in $R$ plots)

>>>>

   	\begin{figure}[htb]
   		\centering
   		\includegraphics[scale=0.07]{Figs/3PARToSched.jpg}
   		\caption{ \label{fig:firstSegment} First segment of Schedule $S$}
   	\end{figure}

@@

	\todo[inline]{SKumar: Evaluate different metrics for HF, Cholesky and CCSD applications}
	\todo[inline]{SKumar: decide metrics: ratio to optimal, percentage overlap, 100 - percentage non overlap}
	\begin{itemize}
		\item Machine description
		\item temporary data requirement
		\item Description of all kernels (Molecular Chemistry Kernels)
		\item Think about results and graphs (Most probably results in $R$ plots)
	\end{itemize}
\newpage
The following table exhibits favorable scenarios for different heuristics. This table allows programmers to use appropriate strategies to maximize communication-computation overlap for their applications.

\begin{table}[htb]
	\scriptsize
	\begin{tabular}{|c|p{3cm}|}
		\hline
		\textbf{Heuristic} & \textbf{Favorable Situation} \\ \hline
		order\_of\_optimal\_strategy\_infinite\_memory & Unlimited memory capacity (\textcolor{green}{Optimal}) \\ \hline
		increasing\_order\_of\_communication\_strategy & Unlimited memory capacity and tasks are compute intensive (\textcolor{green}{Optimal}) \\ \hline
		decreasing\_order\_of\_computation\_strategy & Unlimited memory capacity and tasks are communication intensive (\textcolor{green}{Optimal}) \\ \hline
		increasing\_order\_of\_communication\_plus\_computation\_strategy & Moderate memory capacity and most tasks are compute intensive \\ \hline
		decreasing\_order\_of\_communication\_plus\_computation\_strategy & Moderate memory capacity and most tasks are communication intensive \\ \hline
		largest\_communication\_task\_respects\_memory\_restriction &  Limited memory capacity and significant percentage of tasks are communication intensive \\ \hline
		smallest\_communication\_task\_respects\_memory\_restriction & Limited memory capacity and most tasks are compute intensive \\ \hline
		maximum\_accelerated\_task\_respects\_memory\_restriction &  Limited memory capacity and number of communication and compute intensive tasks are approximately equal \\ \hline
		optimal\_order\_infinite\_memory\_largest\_communication\_task\_respects\_memory\_restriction & Moderate memory capacity and significant percentage of tasks are communication intensive\\ \hline
		optimal\_order\_infinite\_memory\_smallest\_communication\_task\_respects\_memory\_restriction & Moderate memory capacity and most tasks are compute intensive \\ \hline
		optimal\_order\_infinite\_memory\_maximum\_accelerated\_task\_respects\_memory\_restriction & Moderate   memory capacity and number of communication and compute intensive tasks are approximately equal \\ \hline
	\end{tabular}\caption{~\label{tab:heuristicsAndFavorableScenarios}Heuristics and their favorable scenarios}
\end{table}

Here moderate memory capacity refers to limited capacity but close to the maximum memory  requirement of the considered application.

\newpage
